D.I.A.G.R.A.M.: Development of Image Analysis for Graph Recognition And Modeling

### 2025-06-29 doc/article/article.tex
Update paper

\subsection{Object Detection}
TODO

@@

\section{ArrowNet}
\label{arrow-net}

This second approach for determining an arrow's orientation was inspired by UNet \cite{unet}. The core idea was to segment an arrow's bounding box, and to use a specific CNN to try and determine the arrow's head point and the arrow's tail point. The downsampling-upsampling network is called \textbf{ArrowNet} and its specifics can be found in Table~\ref{table:arrownet}.

\begin{table}[htbp]
	\centering
	\caption{ArrowNet Architecture Details}
	\label{tab:arrownet}
	\begin{tabular}{|l|l|l|l|l|}
		\hline
		\textbf{Stage} & \textbf{Layer} & \textbf{Out Channels} & \textbf{Operations} \\
		\hline
		\multirow{3}{*}{Encoder} 
		& Encoder1 & $32$ & Double Conv Block \\
		& MaxPool & $32$ & $2 \times 2$ MaxPooling \\
		& Encoder2 & $64$ & Double Conv Block \\
		\hline
		Bottleneck 
		& MaxPool + Bottleneck & $128$ & MaxPool + Double Conv \\
		\hline
		\multirow{4}{*}{Decoder}
		& Upsampling2 & $64$ & Transpose Conv Block \\
		& Skip + Decoder2 & $64$ & Concat + Double Conv \\
		& Upsampling1 & $32$ & Transpose Conv Block \\
		& Skip + Decoder1 & $32$ & Concat + Double Conv \\
		\hline
		Output & Output Conv & $3$ & $1 \times 1$ Convolution \\
		\hline
	\end{tabular}
	\label{table:arrownet}
\end{table}

@@

\begin{table}[h]
	\centering
	\caption{Classification Network Details}
	\label{tab:classification-architecture}
	\begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{Conv Layer} & \textbf{Output Channels} & \textbf{Kernel Size} & \textbf{Pool Kernel Size} \\
		\hline 
		1 & 8 & 2 & 3 \\
		2 & 16 & 2  & 3 \\
		3 & 24 & 3  & 2 \\
		\hline
		\textbf{Linear Layer} & \textbf{Output Features} & \textbf{Droput Rate} & \textbf{Activation Function} \\
		\hline 
		1 & 2048 & 0.2 & ReLU \\
		2 & 128 & 0.2 & ReLU \\
		3 & 3 & 0.2 & ReLU \\
		\hline
	\end{tabular}
\end{table}

>>>>

\subsection{Object Detection}

TODO: Talk about the net.

The model employed was tested in two different ways: as zero-shot, after a 10-epoch training and after a 100-epoch training. The best-behaving one was, of course, the latter. In Table~\ref{tab:map} and Table~\ref{tab:mar} we show the Mean Average Precision and Recall of the model used.

\begin{table}[htbp]
	\centering
	\caption{Mean Average Precision (\textit{mAP}) Metrics}
	\begin{tabular}{|l|c|l|}
		\hline
		\textbf{Metric} & \textbf{Value} & \textbf{Description} \\
		\hline
		mAP & 0.8754 & Overall mean Average Precision \\
		mAP@0.5 & 0.9878 & mAP at IoU threshold 0.5 \\
		mAP@0.75 & 0.9183 & mAP at IoU threshold 0.75 \\
		\hline
		mAP (Small) & 0.6444 & mAP for small objects \\
		mAP (Medium) & 0.8054 & mAP for medium objects \\
		mAP (Large) & 0.8975 & mAP for large objects \\
		\hline
	\end{tabular}
	\label{tab:map}
\end{table}

\begin{table}[htbp]
	\centering
	\caption{Mean Average Recall (\textit{mAR}) Metrics}
	\label{tab:mar}
	\begin{tabular}{|l|c|l|}
		\hline
		\textbf{Metric} & \textbf{Value} & \textbf{Description} \\
		\hline
		mAR@1 & 0.3436 & mAR with max 1 detection per image \\
		mAR@10 & 0.8877 & mAR with max 10 detections per image \\
		mAR@100 & 0.9128 & mAR with max 100 detections per image \\
		\hline
		mAR (Small) & 0.6631 & mAR for small objects \\
		mAR (Medium) & 0.8670 & mAR for medium objects \\
		mAR (Large) & 0.9141 & mAR for large objects \\
		\hline
	\end{tabular}
\end{table}

Furthermore, we also think that the following metrics show a great precision:

\begin{itemize}
	\item \textbf{Average X-axis error:} 6.84 pixels
	\item \textbf{Average Y-axis error:} 4.84 pixels
\end{itemize}

@@

\section{ArrowNet}
\label{arrow-net}
This second approach for determining an arrow's orientation was inspired by UNet \cite{unet}. The core idea was to segment an arrow's bounding box, and to use a specific CNN to try and determine the arrow's head point and the arrow's tail point. This downsampling-upsampling network is called \textbf{ArrowNet} and its specifics can be found in Table~\ref{table:arrownet}.

\begin{table}[htbp]
	\centering
	\caption{ArrowNet Architecture Details}
	\label{tab:arrownet}
	\begin{tabular}{|l|l|l|l|l|}
		\hline
		\textbf{Stage} & \textbf{Layer} & \textbf{Out Ch} & \textbf{Operations} \\
		\hline
		\multirow{3}{*}{Encoder} 
		& Encoder1 & $32$ & Double Conv Block \\
		& MaxPool & $32$ & $2 \times 2$ MaxPooling \\
		& Encoder2 & $64$ & Double Conv Block \\
		\hline
		Bottleneck 
		& MaxPool+Bottleneck & $128$ & MaxPool+Double Conv \\
		\hline
		\multirow{4}{*}{Decoder}
		& Upsampling2 & $64$ & Transpose Conv Block \\
		& Skip + Decoder2 & $64$ & Concat + Double Conv \\
		& Upsampling1 & $32$ & Transpose Conv Block \\
		& Skip + Decoder1 & $32$ & Concat + Double Conv \\
		\hline
		Output & Output Conv & $2$ & $1 \times 1$ Convolution \\
		\hline
	\end{tabular}
	\label{table:arrownet}
\end{table}

The entire architecture is composed of three main building blocks:

\begin{enumerate}
\item \textbf{Double Convolution Block:} Each double convolution block applies two consecutive $3 \times 3$ convolutions with padding 1, followed by batch normalization, and a ReLU activation after each convolution. This should preserve spatial dimensions while increasing feature depth.

\item \textbf{Upsampling Block:} The upsampling blocks use $2 \times 2$ transposed convolutions with stride 2, followed by batch normalization and ReLU activation.

\item \textbf{Skip Connections:} The architecture employs skip connections that concatenate feature maps from the encoder path with corresponding decoder features.

\end{enumerate}

The two output float channels of ArrowNet should have been used to predict, in a given position: $1$ if the head's point is in a certain position, $0$ else; $1$ if the tail's point is in a certain position, $0$ else - for the first and second channel respectively.

\begin{figure}[H]
	\centering
	\includegraphics[width=225pt, height=75pt]{arrownet1.jpg}
	\caption{Some results for arrow's head reconstruction.}
	\label{fig:arrownet1}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=225pt, height=75pt]{arrownet2.jpg}
	\caption{The overall result of an ArrowNet input.}
	\label{fig:arrownet2}
\end{figure}

As seen in Figure~\ref{fig:arrownet2}, due to the low number of samples in the dataset, the network is unable to correctly distinguish between an arrow's head and tail.

@@

The \textbf{Classification Network} is a lightweight convolutional neural network, suited for processing grayscale images. The architecture is composed of convolutional feature extraction layers followed by fully connected classification layers. Some specific about it can be found in Table~\ref{tab:classification-architecture}.

\begin{table}[h]
	\centering
	\caption{Classification Network Details}
	\label{tab:classification-architecture}
	\begin{tabular}{|c|c|c|c|}
		\hline
		\textbf{Layer Type} & \textbf{Out Channels} & \textbf{Kernel Size} & \textbf{Pool Kernel Size} \\
		\hline 
		Conv & 8 & 2 & 3 \\
		Conv & 16 & 2  & 3 \\
		Conv & 24 & 3  & 2 \\
		\hline
		\textbf{Layer Type} & \textbf{Out Features} & \textbf{Droput Rate} & \textbf{Activation Function} \\
		\hline 
		Linear & 2048 & 0.2 & ReLU \\
		Linear & 128 & 0.2 & ReLU \\
		Linear & 3 & 0.2 & ReLU \\
		\hline
	\end{tabular}
\end{table}
